### 2024-08-23 mycv/subs/papers.tex
updates in the status of Cermet paper
Updates

  {Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}
  {submitted}

@@

  {submitted}

@@

  {submitted}

>>>>

@@

  {Accepted}

@@

  {in-press}
  {\ref{https://doi.org/10.1016/j.ijplas.2024.104032}{Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}}
  {Vol. 179, 104032, 2024}
